Pillar 1 - Sequential Pattern Mining

### 2019-02-15 Pillar 1 - Sequential Pattern Mining.Rmd
save cached results in folder `Cache`

@@

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE, warning = FALSE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%

>>>>

```{r setup, include = T}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
```

@@

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```
####Save d_transactions
```{r save d_transaction}
save(
  d_transactions,
  file = "Output/transaction_df.RDATA"
  )
```
### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE, warning = FALSE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%
